The Impact of Uncertainty on Monetary Transmission

### 2023-10-25 US/draft.Rmd
Tidied granger causality table

```{=latex}
\begin{center}
`r xtable::xtable(read_rds('data/granger.rds'), type = "latex", digits = 3, align = c("p{0.1cm}", "p{9cm}", "p{2cm}", "p{2cm}"),label = 'tab:grang', caption = 'Granger causality tests with alternative model specifications',
display = c('g', 'g', 'g', 'g'))`
\end{center}
```
The results of these tests suggests that in most cases we fail to reject the null, and thus policy shocks do not drive uncertainty, neither the other way around. Interpreting the p-values as the likelihood of $H0$ to be true, there are a handful of conclusions to draw. The likelihood of policy shocks driving uncertainty stay reasonably high irrespective of specification, however, for the reverse causality case, it varies substantially. Firstly, the likelihood of uncertainty being a driver of policy shocks considerably increases when switching from the median to the 70th percentile threshold. This is likely due to the low number of observations in the regime, and thus an increased likelihood of policy action being taken to mitigate the negative impact of uncertainty. Secondly, using the Shadow rate[^7] over the FFR also considerably reduces this likelihood. Given these, the superior specification should be a TVAR with a full set of controls estimated with the threshold level set to the median. The next subsection showcases the impulse responses estimated from this.

>>>>

```{=latex}
\begin{center}
`r xtable::xtable(read_rds('data/granger.rds'), type = "latex", digits = 3, align = c("p{0.1cm}", "p{9cm}", "p{2cm}", "p{2cm}"),label = 'tab:grang', caption = 'Granger causality tests with alternative model specifications',
display = c('g', 'g', 'g', 'g'))`

\bgroup

\renewcommand{\baselinestretch}{0.75}\normalsize
\textit{Notes:} \linebreak
Test 1: $H_{0}$: Shock does not cause uncertainty \linebreak
Test 2: $H_{0}$: Uncertainty does not cause shock

\egroup

\end{center}
```

The results of these tests suggests that in most cases we fail to reject the null, and thus policy shocks do not drive uncertainty, neither the other way around. Interpreting the p-values as the likelihood of $H_{0}$ to be true, there are a handful of conclusions to draw. The likelihood of policy shocks driving uncertainty stay reasonably high irrespective of specification, however, for the reverse causality case, it varies substantially. Firstly, the likelihood of uncertainty being a driver of policy shocks considerably increases when switching from the median to the 70th percentile threshold. This is likely due to the low number of observations in the regime, and thus an increased likelihood of policy action being taken to mitigate the negative impact of uncertainty. Secondly, using the Shadow rate[^7] over the FFR also considerably reduces this likelihood. Given these, the superior specification should be a TVAR with a full set of controls estimated with the threshold level set to the median. The next subsection showcases the impulse responses estimated from this.
